Quality Criteria for SKOS Vocabularies

### 2012-03-22 analysis.tex
added missing wcc analysis numbers
added all criteria to table to better estimate space left
added comments/updated result table
added TODO

\subsection{Vocabulary Data Set}
Our vocabulary dataset covers XY vocabularies from various domains differing in statistical properties (cf. Table~\ref{vocabs}). The data was gathered in different ways. Some vocabularies where downloaded from their respective project websites or, in the cases of IPSV, Peroxisome Knowledge Base, and LVAk requested directly from the creators. The MeSH dataset was created by \cite{Assem2006} and is available for download\footnote{\url{http://thesauri.cs.vu.nl/eswc06/}}. We created the SKOS version of LVAk thesaurus from CSV files provided by the vocabulary maintainers. The vocabulary structure was uncomplex, so the conversion process to SKOS turned out as being rather straightforward.

@@

@@

\begin{table}[h]
\caption{Results of the proposed metrics}
\begin{tabular}{p{4cm}ccccccccccccccc}
\textbf{Metric} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
\toprule
Loose Concepts & 162000 & 671 & 0 & 2 & 7 & 0 & 0 & 77062 & 1125 & 4979 & 172364 & 0 & 4 & 0 & 21 \\
Weakly Connected Components & 621 & 0 & & & 4 & 1 & 4 && 0 & 0 && 5 & 1 & 1 & 11 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\subsection{Vocabulary Data Set}

Our vocabulary dataset covers XY vocabularies from various domains differing in statistical properties (cf. Table~\ref{vocabs}). The data was gathered in different ways. Some vocabularies where downloaded from their respective project websites or, in the cases of IPSV, Peroxisome Knowledge Base, and LVAk requested directly from the creators. The MeSH dataset was created by \cite{Assem2006} and is available for download\footnote{\url{http://thesauri.cs.vu.nl/eswc06/}}. We created the SKOS version of LVAk thesaurus from CSV files provided by the vocabulary maintainers. The vocabulary structure was uncomplex, so the conversion process to SKOS turned out as being rather straightforward.

@@

\todo{CM}{skip domain classification; this looks inconsistent and takes space.}

@@

\begin{table}[h]
\caption{Results of the proposed metrics}
\begin{tabular}{p{4cm}ccccccccccccccc}
\textbf{Metric} & \rotatebox{90}{\textbf{GTAA}} & \rotatebox{90}{\textbf{Geonames}} & \rotatebox{90}{\textbf{MeSH}} & \rotatebox{90}{\textbf{PXV}} & \rotatebox{90}{\textbf{Eurovoc}} & \rotatebox{90}{\textbf{IPSV}} & \rotatebox{90}{\textbf{Agrovoc}} & \rotatebox{90}{\textbf{DBpedia}} & \rotatebox{90}{\textbf{Pressinfo}} & \rotatebox{90}{\textbf{NYTP}} & \rotatebox{90}{\textbf{LCSH}} & \rotatebox{90}{\textbf{Meketre}} & \rotatebox{90}{\textbf{STW}} & \rotatebox{90}{\textbf{NAICS}} & \rotatebox{90}{\textbf{LVAk}} \\
\toprule
Omitted or Invalid Language Tags &&&&&&&&&&&&&&& \\

Incomplete Language Coverage &&&&&&&&&&&&&&& \\

Undocumented Concepts &&&&&&&&&&&&&&& \\

Label Conflicts &&&&&&&&&&&&&&& \\

\midrule

Loose Concepts & 162000 & 671 & 0 & 2 & 7 & 0 & 0 & 77062 & 1125 & 4979 & 172364 & 0 & 4 & 0 & 21 \\

Weakly Connected Components & 621 & 0 & & 10 & 4 & 1 & 4 & 1506 & 0 & 0 & 22131 & 5 & 1 & 1 & 11 \\

Cyclic Hierarchical Relations &&&&&&&&&&&&&&& \\

Valueless Associative Relations &&&&&&&&&&&&&&& \\

Solely Transitively Related Concepts &&&&&&&&&&&&&&& \\

Omitted Top Concepts &&&&&&&&&&&&&&& \\

Top Concept Having Broader Concepts &&&&&&&&&&&&&&& \\

\midrule

Missing In-Links &&&&&&&&&&&&&&& \\

Missing Out-Links &&&&&&&&&&&&&&& \\

Link Target Unavailability &&&&&&&&&&&&&&& \\

\midrule

Undefined SKOS Property Usage &&&&&&&&&&&&&&& \\

\bottomrule
\end{tabular}
\end{table}
